A Standard for the Scholarly Citation of Archaeological Data

### 2017-10-03 analysis/paper/paper.Rmd
2nd go at crevents

saveRDS(events, "../data/raw_data/cross_ref_events.rds")

# Extract dataframes for analysis
events_df <- 
map_df(events, ~.x$result$message$events)

>>>>

# saveRDS(events, "../data/raw_data/cross_ref_events_2017_09_03.rds")
# events <- read_rds("../data/raw_data/cross_ref_events.rds")

# Extract dataframes for analysis
events_df <- 
map_df(events, ~.x$result$message$events)
# 366 obs 2 Oct
# 367 obs 3 Oct
